The universal property of direct integrals in W$^*$-categories

### 2018-10-21 direct_integrals.tex
preliminary stuff on measurable families

% general mathematical macros
\renewcommand{\H}{\mathcal{H}}	% Hilbert space
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Rplusext}{\overline{\mathbb{R}}_+} % extended nonnegative reals, as where measures take values
\newcommand{\C}{\mathbb{C}}
\newcommand{\op}{\mathrm{op}}
\newcommand{\eps}{\varepsilon}
\newcommand{\lin}[1]{\mathrm{lin}(#1)}
\newcommand{\dom}[1]{\mathrm{dom}(#1)} 		% domain of a morphism
\newcommand{\cod}[1]{\mathrm{cod}(#1)} 		% codomain of a morphism
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\esssup}{\mathrm{ess\, sup}} 	% essential supremum

@@

@@

\author{Tobias Fritz, Robert Furber, Bas Westerbaan}

\address{Max Planck Institute for Mathematics in the Sciences, Leipzig, Germany}
\email{fritz@mis.mpg.de}

@@

\thanks{\textit{Acknowledgements.} }

@@

\newcommand{\Obj}[1]{\mathrm{Obj}(#1)}
\newcommand{\Mor}[1]{\mathrm{Mor}(#1)}

@@

Now let $\cat{C}$ be a W$^*$-category, and $X \in \LMeas$. Then we define a category $L^\infty(X,\cat{C})$ as follows:

\begin{enumerate}
\item Objects are maps $A : X \to \cat{C}, \: x\mapsto A_x$, which are measurable in the sense that there is a measurable partition of $X$ such that $A$ is constant on each part;
\item Morphisms $f : A\to B$ are equivalence classes of bounded families $(f_x : A_x\to B_x)_{x\in X}$, which depend measurably \todo{work out what exactly this should mean such that composition makes sense} on $x$, and where $f \sim g$ if upon restriction to any measurable set on which both $A$ and $B$ are constant, we have $f^{-1}(T) \triangle g^{-1}(T) \in \Null_X$ for every measurable $T \subseteq \cat{C}(A,B)$.
\end{enumerate}

>>>>

% general mathematical macros
\renewcommand{\H}{\mathcal{H}}	% Hilbert space
\newcommand{\B}[1]{\mathcal{B}(#1)}	% bounded operators
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Rplusext}{\overline{\mathbb{R}}_+} % extended nonnegative reals, as where measures take values
\newcommand{\C}{\mathbb{C}}
\newcommand{\op}{\mathrm{op}}
\newcommand{\eps}{\varepsilon}
\newcommand{\lin}[1]{\mathrm{lin}(#1)}
\newcommand{\dom}[1]{\mathrm{dom}(#1)} 		% domain of a morphism
\newcommand{\cod}[1]{\mathrm{cod}(#1)} 		% codomain of a morphism
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\esssup}{\mathrm{ess\, sup}} 	% essential supremum

@@

\newcommand{\Obj}[1]{\mathrm{Obj}(#1)}	% collection of objects of a cat
\newcommand{\Mor}[1]{\mathrm{Mor}(#1)}	% collection of morphisms of a cat

@@

\author{Tobias Fritz}
\author{Robert Furber}
\author{Bas Westerbaan}

\address{Perimeter Institute for Theoeretical Physics}
\email{tfritz@pitp.ca}

\address{add your affiliation here}

@@

\thanks{\textit{Acknowledgements.} Part of this work was conducted while the first author was at the Max Planck Institute for Mathematics in the Sciences in Leipzig, Germany.}

@@

@@

\todo[inline]{T: The following is all still tentative}

Now let $X \in \LMeas$, and let $\cat{C}$ be a W$^*$-category. We say that $\cat{C}$ is a \emph{measurable W$^*$-category} if both objects and morphisms form (potentially large) measurable spaces, and such that all structure maps, including the involution, are measurable; we also require that the restriction to each hom-set $\cat{C}(A,B)$ recovers the Borel (or Baire?) $\sigma$-algebra.

\begin{ex}
$\NRep{\cat{N}}$ has a canonical measurable structure of this kind if we declare a collection of objects $\mathcal{S}$ to be measurable if for every Hilbert space $\H$, the set of all $\pi : \cat{N} \to \B{\H}$ which are in is $\mathcal{S}$ is measurable, in the sense of the smallest $\sigma$-algebra which makes the evaluation maps $\pi \mapsto \langle \xi,\pi(a) \xi\rangle$ for $\xi\in\H$ and $a\in\cat{N}$ measurable. As a degenerate special case, for $\cat{C} = \Hilb$ we obtain the discrete $\sigma$-algebra on the objects.

\todo[inline]{Throughout this example, would it be better to use Borel/Baire $\sigma$-algebras instead?}

On morphisms, we likewise define a collection of morphisms $\mathcal{T}$ to be measurable if for every two Hilbert spaces $\H_1,\H_2$, the set of all triples $(\pi_1,\pi_2,f)$ with $f : \H_1 \to \H_2$ intertwining $\pi_1 : \cat{N} \to \B{\H_1}$ and $\pi_2 : \cat{N} \to \B{\H_2}$ is measurable in the smallest $\sigma$-algebra which makes the three projection maps measurable, where the first two projections map to the space of normal representations on a Hilbert space, where we use the $\sigma$-algebra from the previous paragraph; the third projection maps to $\Hilb(\H_1,\H_2)$, where we similarly use the $\sigma$-algebra generated by the evaluation maps $f \mapsto \langle \zeta, f \xi\rangle$.

\todo[inline]{This does not seem to make composition measurable}
\end{ex}

In general, we then define a category $L^\infty(X,\cat{C})$ as follows:

\begin{enumerate}
\item Objects are measurable maps $A : X \to \cat{C}, \: x\mapsto A_x$;
\item Morphisms $f : A\to B$ are equivalence classes of bounded families $(f_x : A_x\to B_x)_{x\in X}$, which depend measurably on $x$, and where equivalence $f \sim g$ means that $f^{-1}(T) \triangle g^{-1}(T) \in \Null_X$ for every measurable $T \subseteq \Mor{\cat{C}}$.
\end{enumerate}
